Bayesian Graphical Entity Resolution using Exchangeable Random Partition Priors

### 2021-10-14 bayesian-analysis/kundinger-ba-2021.tex
update.

\begin{frontmatter}
\title{Efficient and Scalable Bipartite Matching with Fast Beta Linkage  (fabl)}
%\title{\support{}}
\runtitle{Efficient and Scalable Bipartite Matching with Fast Beta Linkage  (fabl)}

\begin{aug}
%\author{\fnms{} \snm{}}
%\author{\fnms{<firstname>} \snm{<surname>}\thanksref{}\ead[label=e1]{}}
%\and
%\author{\fnms{} \snm{}}

\runauthor{}

\address[addr1]{}

>>>>

\begin{frontmatter}
\title{Bayesian Graphical Entity Resolution using Exchangeable Random Partition Priors}
%\title{A Sample Document\thanksref{T1}}
%\thankstext{T1}{<thanks text>}
\runtitle{Entity Resolution using Exchangeable Random Partition Priors}

\begin{aug}
\author{\fnms{Brian} \snm{Kundinger}\thanksref{addr1}\ead[label=e1]{brian.kundinger@duke.edu}},
\author{\fnms{Jerome} \snm{Reiter}\thanksref{addr1}\ead[label=e2]{jerry@stat.duke.edu}}
\and
\author{\fnms{Rebecca C.} \snm{Steorts}\thanksref{addr2}\ead[label=e3]{beka@stat.duke.edu}}

\runauthor{Brian Kundinger et al.}

\address[addr1]{Department of Statistical Science,
 Duke University,
  P.O.\ Box 90251,
  Durham, NC 27708, USA
  \printead*{e1}, % print email address of "e1"
  \printead*{e2}
   \printead*{e3}
}

%\address[addr2]{Departments of Statistical Science and Computer Science,
%  Duke University,
%  P.O.\ Box 90251,
%  Durham, NC 27708, USA
%  \printead{e3}
%}
